Work Fragmentation in Developer Interaction Data

### 2016-02-10 paper_2.tex
RQ2 - Effect size table UDC

The Figure \ref{fig:lines_dur_int} shows the median of the metrics when grouping the sessions by the number of interruptions and the proportion of prolonged interruptions with Mylyn, and the Figure \ref{fig:udc_lines_dur_int} with UDC. In this context, it is better to have a low number of interruptions (group [1-3]) and a low proportion of prolonged interruptions, and the results agree with this statement. For example, when having between 1 to 3 interruptions and a low proportion the metrics show higher values when compared to having $>$ 6 interruptions and a high proportion of prolonged interruptions. Moreover, if we focus on a category we can see a gradual decrease as the number of interruptions increases, which lead us to conclude that the proportion of prolonged interruptions has an effect on the developer productivity.

@@

Comparing the results between the datasets, UDC seems to show a more defined difference between groups. The sessions with a low proportion of prolonged interruption has a greater difference (higher productivity) than sessions with medium proportion. In Mylyn this difference is more subtle but can be identified.

@@

>>>>

The Figure \ref{fig:lines_dur_int} shows the median of the metrics when grouping the sessions by the number of interruptions and the proportion of prolonged interruptions with Mylyn, and the Figure \ref{fig:udc_lines_dur_int} with UDC. In this context, it is better to have a low number of interruptions (group [1-3]) and a low proportion of prolonged interruptions, and the results agree with this statement. For example, when having between 1 to 3 interruptions and a low proportion the metrics show higher values when compared to having $>$ 6 interruptions and a high proportion of prolonged interruptions. Moreover, if we focus on a category we can see a gradual decrease as the number of interruptions increases, which lead us to conclude that the proportion of prolonged interruptions has an effect on the developer productivity. In the Figures the color of lines represent a classificacion of the proportion of prolonged interruptions, being the green line the 'low' type, blue the 'medium' and red the 'high'.

@@

Comparing the results between the datasets, UDC seems to show a more defined difference between groups. The sessions with a low proportion of prolonged interruption has a greater difference (higher productivity) than sessions with medium proportion. In Mylyn this difference is more subtle but can be identified, although when having more than 6 interruptions there is not a real difference.

@@

\begin{table}[ht!]
\tiny
\renewcommand{\arraystretch}{1.3}
\caption{Effect size and statistical significance of the relationships between edits and selection per minute, edit ratio, and duration of interruptions in UDC} %, and editions and selections.}
\label{tbl:p_value2}
\centering
\begin{tabular}{l | p{0.7cm} | p{1cm} | p{1cm} | p{1cm} } 
  & none & low & medium & high  \\  
  \hline
  \multicolumn{5}{c}{\textbf{Edits}} \\
  \hline
  mean & 4.01 &	2.31 & 1.94 & 2.06 \\ 
  % \cline{3-4} 
  %t.test & $\hookrightarrow$& \multicolumn{2}{c}{$<$ 2.2e-16} \\
   \cline{3-5} 
  U-test & $\hookrightarrow$ & \multicolumn{3}{c}{$<$ 2.2e-16}  \\

  \cline{3-5} 
  Cohen's $d$ & $\hookrightarrow$	& \textbf{0.75} & \textbf{0.89} & \textbf{0.70}  \\
  \hline

  \multicolumn{5}{c}{\textbf{Selections}} \\
  \hline 
  mean & 2.99 &	2.08 & 1.85 & 1.97 \\ 
  % \cline{3-4} 
  %t.test & $\hookrightarrow$& 2.089e-08 & 8.175e-14 \\
   \cline{3-5} 
  U-test & $\hookrightarrow$ & 8.467e-13 & \multicolumn{2}{c}{$<$ 2.2e-16}  \\

  \cline{3-5} 
  Cohen's $d$ & $\hookrightarrow$	& \textbf{0.53} & \textbf{0.69} & \textbf{0.49} \\  
  \hline
  \multicolumn{5}{c}{\textbf{Edit ratio}} \\
  \hline 
  mean & 0.56 & 0.49 & 0.45 & 0.44 \\ 
%   \cline{3-4} 
%  t.test & $\hookrightarrow$&  4.20E-12 & $<$ 2.2e-16 \\
   \cline{3-5} 
  U-test & $\hookrightarrow$ & 6.467e-05 & 2.095e-08 & 1.218e-09 \\
  \cline{3-5} 
  Cohen's $d$ & $\hookrightarrow$ & \textbf{0.29} & \textbf{0.41} & \textbf{0.45}\\
\hline
